Aggregated Product System Models in Life Cycle Assessment: Transparency versus Privacy

### 2017-10-17 aggregation/agg-JIE.tex
Morning work on agg math
foreground work

\input{psstyle}
\input{draw-matrices}

\title{Structured Representation of Aggregated Product System Models in Life Cycle Assessment}
\author{Brandon Kuczenski\\
Institute for Social, Behavioral, and Economic Research\\
University of California, Santa Barbara}
\date{\mydate\today}

@@

  \maketitle
  %\emph{For submission to the Journal of Industrial Ecology; February 2017}

@@

@@

  \input{publication-objective}

  \input{publication-method}

  \input{publication-components}

  \input{publication-foreground}

  \input{publication-example}

  \input{publication-discussion}

  \input{publication-conclusion}

  \input{publication-acknowledgments}

@@

%\mainpaper
\supporting

>>>>

\input{psstyle}
\input{../manuscript/draw-matrices}

\title{Aggregated Product System Models in Life Cycle Assessment: Transparency versus Privacy}
\author{Brandon Kuczenski\\
Institute for Social, Behavioral, and Economic Research\\
University of California, Santa Barbara}
\date{\mydate\today}

@@

  \maketitle
  \emph{For submission to the Journal of Industrial Ecology; October 2017}

@@

  {\red http://pubs.acs.org/doi/pdf/10.1021/acs.est.5b01558}

@@

  \input{agg-objective}

  \input{agg-basic-lca}

  \input{agg-lca-study}

  %% \input{publication-foreground}

  %% \input{publication-example}

  %% \input{publication-discussion}

  %% \input{publication-conclusion}

  %% \input{publication-acknowledgments}

@@

\mainpaper
%\supporting

### 2017-10-17 aggregation/agg-abstract.tex

\begin{abstract}
  Many of the challenges facing %interpretation and
  knowledge synthesis from life cycle assessment (LCA) studies stem from the inability of study authors and readers to formally agree on the structure and content of life cycle inventory models.  This article presents a framework for LCA study authors to publish inventory models in a structured format based on a mathematical formulation of a \emph{foreground study}.  Using linked semantic data as a foundation, the publication framework %offers a mechanism to provide
  provides for both machine readability and unambiguous human interpretation of published studies.  To implement the framework, the LCA community should find ways to enable study authors and data users to make common reference to shared data sources, including background databases, elementary flows, and impact assessment methods, that are widely used in many studies.  The framework contributes to ongoing efforts within industrial ecology to improve the reproducibility and verifiability of scholarly works, and if implemented, plots a course toward distributed, platform-independent computation and validation of LCA results.
\end{abstract}

>>>>

\begin{abstract}
  Many of the challenges facing %interpretation and
  knowledge synthesis from life cycle assessment (LCA) studies stem from the inability of study authors and readers to formally agree on the structure and content of life cycle inventory models.  This article presents a framework for computing aggregation results in LCA $\ldots$
\end{abstract}
